---
title: "Figure 6"
author: "Luciano Moffatt"
date: "`r Sys.Date()`"
output: pdf_document
---


```{r setup}
library(readr)
library(tidyverse)
library(envalysis)
library(patchwork)
library(cowplot)
library(HDInterval)
if (!requireNamespace("ConformationalModel", quietly = TRUE)) {
  if (!requireNamespace("devtools", quietly = TRUE)) {
    install.packages("devtools")
  }
  devtools::install_github("lmoffatt/ConformationalModel")
}
library(ConformationalModel)
library(ggimage)
library(thirdAxis)
library(xtable)
library(cowplot)
```



Figure 6 . The driving idea is how to get to the likelihood calculation. 

First we show how the model predict the unitary current as a function of the number of rotated units. (A)

With this information and the posterior states and the number of channels 
we can predict the current (panel B).

To get to the likelihood we need to model the variance of the predicted current. 
There are three components that might vary with the length of the time interval: the white noise, the pink noise and the stochastic noise . C


We then use this information to calculate the logLikelihood, which could be compared to the expected logLikelihood. D



Lets see the requirements in terms of files of every panel. 

A--> parameters. 

B--> predictions

C--> parameters and states

D--> states


##A



First load the parameters
```{r}
f=c(
  "./r_analysis/data/w9_IE_DR_32c_32s_4b_scheme_10_inact_PI_logbaseline_0_0_scheme_10_inact_c04c49f_192436s748577_10921472283437478284"
)

schemes=c("scheme_10")
algorithms=c("DR")

datas=c("full_experiment")
repetitions=c(1)

```


```{r}
format_significant <- function(x, digits=3) {
  paste0(format(x, digits = digits, scientific = abs(x) >= 1e3 | abs(x) < 1e-2))
}


```




```{r}

d_par=data.frame()

for (i in seq_len(length(f))){
j=10
file<- f[i]
if(file.exists(paste0(file,ifelse(j>0,paste0("_",j),""),"__i_beta__i_walker__i_par.csv"))){
tmp <- try(d_par0<-read.csv(paste0(file,ifelse(j>0,paste0("_",j),""),"__i_beta__i_walker__i_par.csv")))
  if (!inherits(tmp, 'try-error')){
  print(paste0(f[i]," run",j))
  
  d_par0$run=j
 j=j+1
 
while(file.exists(paste0(file,"_",j,"__i_beta__i_walker__i_par.csv"))){
  tmp <- try(d2<-read.csv(paste0(file,"_",j,"__i_beta__i_walker__i_par.csv")))
  
  if (!inherits(tmp, 'try-error')){
  d2$run=j
  d_par0<-bind_rows(d_par0,d2)
  print(paste0(" run",j))
  }
  else
  {
  print(paste0(file,"->error run",j))
    
  }
   j=j+1
 
}
d_par0$scheme=schemes[i]
d_par0$algorithm=algorithms[i]
max_iter=max(d_par0$iter)
d_par0$max_iter=max_iter

d_par0$iter_cat=floor(d_par0$iter/(max_iter+1)*9)



d_par<- bind_rows(d_par,d_par0)

}
else
{
  j=j+1
  print("failed->",paste0(f[i]," run",j))
  
}
}
  
}


```


```{r}
d_prior=data.frame()

for (i in seq_len(length(f))){
d_p <-read.csv(paste0(f[i],"_prior.csv"))
d_p$scheme=schemes[i]
d_p$algorithm=algorithms[i]
d_prior<-bind_rows(d_p,d_prior)
}

```

```{r}
d_prior%>%group_by(scheme, algorithm)%>%summarise(num_param=n())->scheme_par_count
scheme_par_count
```



```{r}
d_prior%>%filter(parameter_transformation!="Fixed", scheme=="scheme_10")->parlist
parlist$parameter_name


```


```{r}
d_par$parameter=parlist$parameter_name[d_par$i_p+1]
d_par$parameter_expected=parlist$transformed_mean[d_par$i_p+1]
d_par<-d_par%>% mutate(parameters=factor(parameter,levels=parlist$parameter_name))
```


```{r}

fig_posteriors<-function(data,param_list, bw, labels=c()){
  
  
  ggplot() +
  geom_freqpoly(data = filter(data,beta==1,parameters %in% param_list), binwidth = bw, aes(10^par_value, after_stat(ndensity), color = scheme)) +
  facet_grid(parameters ~ ., scales = "free", switch = "y", labeller= as_labeller(labels, default = label_parsed)) +
  theme_classic()+
  theme(
    #panel.spacing.x = unit(1, "mm"),
    strip.placement = "outside", # Moves strip to the right
    strip.text.y.left =  element_text(angle = 0, hjust = 1,size = 7) ,# Ensures horizontal orientation
     strip.background = element_blank(),
    axis.text.y = element_blank(), # Removes y-axis text
    axis.title.y = element_blank(), # Removes y-axis title
    axis.ticks.y = element_blank(), 
    axis.line.y = element_blank(), 
    legend.position = "none",
    axis.title.x = element_text(size = 7),       # Axis titles
    axis.text.x = element_text(size = 6),        # Axis labels
    plot.title = element_text(size = 7),        # Optional plot title, if needed
) +
     ylab("parameter value") +
  scale_x_log10(labels = scales::label_log())
}
```





```{r, fig.width=6, fig.height=8}

fig_6A<-function(){

d_par%>% filter((beta == 1.0)|(beta == 0.0), i_par>=10, i_par<13) %>%mutate(parameters=factor(parameter,levels=parlist$parameter_name), tr_par= factor(parameter,labels = parlist$parameter_transformation, levels = parlist$parameter_name), beta=factor(beta),  value= if_else(tr_par=="Log10",10^par_value, par_value) )%>%select(-parameter, - tr_par, -parameter_expected, -i_par, -par_value)%>%pivot_wider(names_from = parameters, values_from = value)%>%mutate(current_max = Leakeage_current_ratio*Rocking_Current_factor^(3)/(1+Leakeage_current_ratio*Rocking_Current_factor^(3)), current_3= Gating_Current, current_2 = Leakeage_current_ratio*Rocking_Current_factor^(2)/(1+Leakeage_current_ratio*Rocking_Current_factor^(2))/current_max*Gating_Current, current_1 = Leakeage_current_ratio*Rocking_Current_factor^(1)/(1+Leakeage_current_ratio*Rocking_Current_factor^(1))/current_max*Gating_Current, current_0 = Leakeage_current_ratio*Rocking_Current_factor^(0)/(1+Leakeage_current_ratio*Rocking_Current_factor^(0))/current_max*Gating_Current, current_2_3= current_2 / current_3, current_1_2 = current_1/current_2, current_0_1 = current_0/current_1)%>%select(-Rocking_Current_factor,-Leakeage_current_ratio,-Gating_Current)%>%pivot_longer(cols = starts_with("current_"),
    )->d_parr0
d_parr0%>%filter(name %in% c("current_0","current_1","current_2","current_3"),iter_cat>7, scheme=="scheme_10")%>%
  mutate(name= recode(name,"current_0"="No rotated subunit",
                      "current_1"="1 rotated subunit", 
                      "current_2"="2 rotated subunits", 
                      "current_3"="3 rotated subunits", 
                      ))%>%
  mutate(name= factor(name, levels=c(
    "3 rotated subunits",
    "2 rotated subunits",
    "1 rotated subunit",
    "No rotated subunit"
    )))  ->d_parr

prior_posterior_color_scale=c("prior"="#D3D3D3", "posterior"="#2C3E50")

return (
ggplot(d_parr)+geom_freqpoly(data=filter(d_parr,beta==1.0, name%in% c("No rotated subunit","1 rotated subunit")),aes(value, after_stat(ndensity),color="posterior"), binwidth=0.0001)+geom_freqpoly(data=filter(d_parr,beta==1.0, !name%in% c("No rotated subunit","1 rotated subunit")),aes(value, after_stat(ndensity),color="posterior"), binwidth=0.05)+
    facet_grid(name ~ ., switch = "y") +
  theme_classic()+
  theme(
    #panel.spacing.x = unit(1, "mm"),
    strip.placement = "outside", # Moves strip to the right
    strip.text.y.left =  element_text(angle = 0, hjust = 1,size = 7) ,# Ensures horizontal orientation
     strip.background = element_blank(),
    axis.text.y = element_blank(), # Removes y-axis text
    axis.title.y = element_blank(), # Removes y-axis title
    axis.ticks.y = element_blank(), 
    axis.line.y = element_blank(), 
    legend.position = "none",
    axis.title.x = element_text(size = 7),       # Axis titles
    axis.text.x = element_text(size = 6),        # Axis labels
    plot.title = element_text(size = 7),        # Optional plot title, if needed
) +
     ylab("parameter value") +
 scale_color_manual(values = prior_posterior_color_scale)+xlab("unitary current (pA)")
)
}
fig_6A()
```


#B




```{r}
d_x=data.frame()

for (i in seq_len(length(f))){
d_x0 <-data.frame()
j = 10
while(file.exists(paste0(f[i],"_",j,"__i_beta__i_walker__i_x.csv"))){
  tmp <- try(d3<-read.csv(paste0(f[i],"_",j,"__i_beta__i_walker__i_x.csv")))
  
  if (!inherits(tmp, 'try-error')){
  d3$run=j
  d_x0<-bind_rows(d_x0,d3)
  print(paste0(f[i]," run",j))
  }
  else
  {
  print(paste0(f[i],"->error run",j))
    
  }
  j=j+1
 
}
d_x0$scheme=schemes[i]
d_x0$algorithm=algorithms[i]
max_iter=max(d_x0$iter)
d_x0$max_iter=max_iter
d_x0$iter_cat=floor(d_x0$iter/(max_iter+1)*9)
d_x<- bind_rows(d_x,d_x0)
}

```




```{r}
file_x= "./experiments/Moffatt_Hume_2007_ATP_time_idealized.txt"

d_y=read.csv(file_x)
i_step_max=max(d_y$i_step,na.rm = T)
i_step_trace=(i_step_max+1)/7; 
d_y$i_trace=floor(d_y$i_step/i_step_trace)  

d_y=left_join(d_y,d_y%>%group_by(i_trace)%>%filter(time-i_trace*121<2, ATP_concentration>0)%>%summarise(t_pulse=min(time)))

d_y$t=d_y$time-d_y$t_pulse



```

```{r}
d_x%>%left_join(d_y, by=join_by(i_step,time), relationship = "many-to-many")->d_x
```

```{r}
ATP_mM=c(0.1,0.2,0.5,1,2,5,10)
d_x$ATP<-factor(ATP_mM[d_x$i_trace+1], levels = ATP_mM)

```
```{r}
d_x$scheme<-factor(d_x$scheme, levels = schemes)

```

```{r}
d_y$ATP<-factor(ATP_mM[d_y$i_trace+1], levels = ATP_mM)

```

```{r,fig.width=10, fig.height=10}}
atp_colors <- c(
  "0.1" = "#BDD7E7",  # Light blue (visible on white)
  "0.2" = "#9ECAE1",  
  "0.5" = "#6BAED6",
  "1"   = "#4292C6",
  "2"   = "#2171B5",
  "5"   = "#08519C",
  "10"  = "#08306B"    # Darkest blue
)
atp_colors <- c(
  "0.1" = "#99C1DA",  # from original "#BDD7E7"
  "0.2" = "#6AAED1",  # from original "#9ECAE1"
  "0.5" = "#1C83BF",  # from original "#6BAED6"
  "1"   = "#0058A7",  # from original "#4292C6"
  "2"   = "#00258D",  # from original "#2171B5"
  "5"   = "#000067",  # from original "#08519C"
  "10"  = "#00001C"   # from original "#08306B"
)
atp_colors <- c(
  "0.1" = "#440154",  # Deep purple, indicating low concentration
  "0.2" = "#31688E",  # Dark blue
  "0.5" = "#21918C",  # Teal
  "1"   = "#35B779",  # Greenish
  "2"   = "#6DCD59",  # Yellow-green
  "5"   = "#B4DE2C",  # Light yellow-green
  "10"  = "#FDE725" # Bright yellow, indicating high concentration
  ,"Current_Noise"  = "gray",
  "Pink_Noise"= "pink"
  )

atp_colors <- c(
  # Viridis-based sequential colors (already colorblind-friendly)
  "0.1" = "#440154",  # Deep purple
  "0.2" = "#31688E",  # Dark blue
  "0.5" = "#21918C",  # Teal
  "1"   = "#35B779",  # Green
  "2"   = "#6DCD59",  # Yellow-green
  "5"   = "#B4DE2C",  # Light yellow-green
  "10"  = "#FDE725",  # Bright yellow
  
  # Categorical noise colors (modified for accessibility)
  "Current_Noise" = "#808080",  # Neutral gray (medium contrast)
  "Pink_Noise"    = "#CC79A7"   # Accessible pink/magenta (from Okabe-Ito)
)
```


```{r,fig.width=10, fig.height=10}}
baseline_current=d_par%>%filter(iter_cat>7, scheme=="scheme_10", parameter=="Current_Baseline")%>%summarise(x=10^median(par_value))%>%pull()
```


```{r,fig.width=10, fig.height=10}}
fig_ATP_pulse<-function(d_y){
  xmin=min(d_y%>%filter(t>0)%>%summarise(min=min(t))%>%pull())
  
  d_y%>%filter(ATP==1)%>%ggplot()+
    geom_step(aes(x=t, y=ATP_concentration/1000), direction = "vh")+
    xlab("time since start of pulse (s)") + 
    ylab("ATP (mM)")+
    coord_cartesian(xlim = c(min(d_y$t), max(d_y$t)), clip = "off") +
 
    scale_color_manual(values = atp_colors)+
    annotate("text",x=xmin, y=1.2,label="0.2-10 mM ATP\n0.2 ms",size=7*25.4 / 72.27, hjust=0, vjust=0)+
    annotate("text",x=10, y=1.2,label="1 mM ATP\n10 ms",size=7*25.4 / 72.27, hjust=0, vjust=0)+
    ylim(0,2)+
    scale_x_log10(limits=c(2e-5,75),labels = scales::label_log())+
    theme_publish()+ 
    theme(legend.position = "none",
              axis.title = element_text(size = 7),       # Axis titles
             axis.text = element_text(size = 7),        # Axis labels
             plot.title = element_text(size = 7),
          plot.margin = margin(
        t=2,
        r=0,
        b = 0,
        l=0,
        unit = "pt"
          ))
}


fig_ATP_pre_pulse<-function(d_y){
  d<-  d_y %>%filter( t< -0.001, ATP==1)
  
  return(d%>%
        ggplot()+
        geom_line(aes(x=-t, y=ATP_concentration))+
        theme_publish()+ 
        ylim(0,2)+
        annotate("text",x=0.5, y=0.2,label="before each ATP pulse",size=7*25.4 / 72.27, hjust=0.5, vjust=0)+  
        scale_x_reverse()+
        xlab("time to pulse (s)") +
        ylab("pulse ATP (mM)")+
          theme(legend.position = "none",
              axis.title = element_text(size = 7),       # Axis titles
             axis.text = element_text(size = 7),        # Axis labels
             plot.title = element_text(size = 7, hjust = -0.35),
             plot.subtitle = element_text(size=7, hjust = -0.12),
             panel.spacing = unit(1,"mm"),
            strip.text.y.left =  element_text(angle = 0, hjust = 1,size = 7) ,# Ensures horizontal orientation
  
          plot.margin = margin(
        t=2,
        r=0,
        b = 0,
        l=0,
        unit = "pt"
      ),
            strip.background = element_blank()
              )+
          scale_color_manual(values = atp_colors)
      )
}
fig_ATP_pre_pulse(d_y)+fig_ATP_pulse(d_y)+plot_layout(design = "
                                                      ABB
                                                      ")


```



```{r,fig.width=10, fig.height=10}}
fig_current_pulse<-function(d_x,alpha){
d<-d_x%>%
    filter( beta==1, t>0, scheme %in%c("scheme_10"),# iter %in% myiters[1:2],
            !is.na(Y_obs))


    ggplot(d)+
   geom_line(data=d%>%filter(t<4),aes(x=t, y=log10(baseline_current-Y_pred), group=interaction(i_trace,iter,i_walker),color=ATP), alpha=alpha)+
   geom_segment(data=d%>%filter(t>2),aes(x=t-10,xend = t+10, y=log10(baseline_current-Y_pred),yend = log10(baseline_current-Y_pred), group=interaction(i_trace,iter,i_walker),color=ATP), alpha=alpha)+
    
      geom_point(aes(x=t, y=log10(baseline_current-Y_obs), color=ATP), size=0.7, alpha=1)+
    scale_y_continuous(limits=c(log10(0.2),NA))+
    scale_x_log10(limits=c(2e-5,75),labels = scales::label_log())+
    theme_publish()+ 
    xlab("time since start of pulse (s)") + 
    ylab(expression(log[10]("mean current (pA)")))+
    theme(legend.position = "none",
              axis.title = element_text(size = 7),       # Axis titles
             axis.text = element_text(size = 7),        # Axis labels
             plot.title = element_text(size = 7),
          plot.margin = margin(
        t=0,
        r=0,
        b = 0,
        l=0,
        unit = "pt"
      ))+
    scale_color_manual(values = atp_colors)
}


fig_current_pre_pulse<-function(d_x,alpha){
  d<-  d_x %>%filter( beta==1,t< -0.001, scheme %in%c("scheme_10")#, iter%in%myiters[1:2]
                   )
  
  return(d%>%
        ggplot()+
        geom_line(aes(x=-t, y=baseline_current-Y_pred, group=interaction(i_trace,iter,i_walker),color=ATP), alpha=alpha)+
        geom_point(aes(x=-t, y=baseline_current-Y_obs, color=ATP), size=0.7)+
        theme_publish()+ 
    scale_y_continuous( breaks=c(0,5) )+
        facet_grid(ATP~.,switch = "y",labeller= as_labeller(
          c("10"="10", "5"="5", "2"="2", "1"="1", "0.5"="0.5", "0.2"="0.2", "0.1"="0.1")
          , default = label_parsed)) +
        scale_x_reverse()+
        xlab("time to pulse (s)") +
        ylab("mean current (pA)")+
        theme(legend.position = "none",
              axis.title = element_text(size = 7),       # Axis titles
             axis.text = element_text(size = 7),        # Axis labels
             plot.title = element_text(size = 7, hjust = -0.35),
             plot.subtitle = element_text(size=7, hjust = -0.12),
             panel.spacing = unit(1,"mm"),
            strip.text.y.left =  element_text(angle = 0, hjust = 1,size = 7) ,# Ensures horizontal orientation
  
          plot.margin = margin(
        t=0,
        r=0,
        b = 0,
        l=0,
        unit = "pt"
      ),
            strip.background = element_blank()
              )+
          scale_color_manual(values = atp_colors)+
      ggtitle("",subtitle = "ATP (mM)" )
      )



}

dx_s<-d_x%>%filter(beta==1,iter_cat>7)
myiters=unique(dx_s$iter)


dd<-dx_s%>%filter(iter%in%sample(myiters,3))
plot_grid(fig_current_pre_pulse(dd,0.1),NULL, fig_current_pulse(dd,0.1)+ggtitle("b"), nrow=1,align = "h", axis = "bt", rel_widths = c(0.5,0,1))

```
```{r}

d_ts=unique(d_y%>%select(t,number_of_samples))%>%filter(number_of_samples>=1)

d_par_noise<-d_par%>%filter(scheme=="scheme_10", beta==1,iter_cat>7, parameter%in%c("Current_Noise","Pink_Noise"))%>%slice_sample(n=1000)%>%select(parameter,iter,beta,iter_cat,i_walker,id_walker,par_value,scheme,algorithm)%>%pivot_wider(names_from = parameter, values_from = par_value)%>%cross_join(d_ts)

figure_variance_pulse<-function(d_x, alpha,maxVar){
fs=50e3

dx_s<-d_x%>%filter(scheme=="scheme_10", beta==1, iter_cat>7, !is.na(Y_var)#, iter %in% myiters[1:2]
                   )

dx_s%>%filter( number_of_samples>=1, t>0, t<4)%>%ggplot()+
  geom_line(aes(x=t,y=log10(Y_var), color=ATP, group=interaction(iter,id_walker,i_trace)), alpha=0.1)+
    geom_segment(data=dx_s%>%filter(t>4),aes(x=t-10,xend = t+10, y=log10(Y_var),yend = log10(Y_var), group=interaction(i_trace,iter,i_walker),color=ATP), alpha=alpha)+
 
  geom_line(data=d_par_noise, aes(x=t, y=log10(10^Current_Noise*fs/number_of_samples), group= interaction(iter,id_walker), color="Current_Noise"), alpha=alpha)+
  geom_line(data=d_par_noise, aes(x=t, y=Pink_Noise, group= interaction(iter,id_walker), color="Pink_Noise"), alpha=alpha)+
  annotate("text", x= 50e-6, y= log10(10), label="white noise",size=7*25.4 / 72.27,vjust=0 )+
  annotate("text", x= 50e-6, y= log10(0.5), label="pink noise",size=7*25.4 / 72.27,vjust=0)+
  scale_x_log10(limits=c(2e-5,75),labels = scales::label_log())+
  scale_y_continuous(limits=c(log10(0.2),log10(maxVar)))+
  scale_color_manual(values = atp_colors)+
  xlab("time from pulse start (s)")+
   ylab( expression(log[10](variance~(pA^2))))+
    theme_classic()+
  theme(legend.position = "none",
         axis.title = element_text(size = 7),       # Axis titles
             axis.text = element_text(size = 7),        # Axis labels
             plot.title = element_text(size = 7),
      plot.margin = margin(
        t=0,
        r=0,
        b = 0,
        l=0,
        unit = "pt"
      ))
}


figure_variance_pre_pulse<-function(d_x, alpha,maxVar){
  fs=50e3

dx_s<-d_x%>%filter(scheme=="scheme_10", beta==1, iter_cat>7, !is.na(Y_var))


dx_s%>%filter( number_of_samples>=10, t<0)%>%ggplot()+
  geom_line(aes(x=-t,y=log10(Y_var), color=ATP, group=interaction(iter,id_walker,i_trace)), alpha=alpha)+
  geom_line(data=d_par_noise%>%filter(t<0), aes(x=-t, y=log10(10^Current_Noise*fs/number_of_samples), group= interaction(iter,id_walker), color="Current_Noise"), alpha=alpha)+
  geom_line(data=d_par_noise%>%filter(t<0), aes(x=-t, y=Pink_Noise, group= interaction(iter,id_walker), color="Pink_Noise"), alpha=alpha)+
  scale_y_continuous(limits=c(log10(0.2),log10(maxVar)))+
  scale_color_manual(values = atp_colors)+
scale_x_reverse()+
        xlab("time to start of ATP pulse (s)") +
        
       ylab( expression(log[10](variance~(pA^2))))+
  theme_classic()+
        theme(legend.position = "none",
             axis.title = element_text(size = 7),       # Axis titles
             axis.text = element_text(size = 7),        # Axis labels
             plot.title = element_text(size = 7, hjust = -0.35),
        plot.margin = margin(
        t=0,
        r=0,
        b = 0,
        l=0,
        unit = "pt"
      ),
          strip.text = element_text(color = "transparent"),
            strip.background = element_blank()
      )  
}
maxVar=max(dx_s$Y_var,na.rm = T)
print(maxVar)
plot_grid(figure_variance_pre_pulse(dd,1,maxVar),NULL, figure_variance_pulse(dd,1,maxVar), nrow=1, rel_widths = c(0.5,0,1))
```

```{r,fig.width=10, fig.height=10}}
ln <- function(x) log(x)

fig_likelihood_pulse<-function(d_x,alpha,minlogL, maxlogL){
d<-d_x%>%
    filter( beta==1, t>0, scheme %in%c("scheme_10"), #iter %in% myiters[1:2],
            !is.na(Y_obs))


    ggplot(d)+
   geom_line(data=d%>%filter(t<4),aes(x=log10(t), y=pelogL, group=interaction(i_trace,iter,i_walker),color=ATP), alpha=alpha)+
  
   geom_segment(data=d%>%filter(t>2),aes(x=log10(t-10),xend = log10(t+10), y=pelogL,yend = pelogL, group=interaction(i_trace,iter,i_walker),color=ATP), alpha=alpha)+
      geom_point(aes(x=log10(t), y=plogL, color=ATP), alpha=alpha, size=0.7)+
    scale_x_continuous(limits=c(log10(2e-5),log10(75)))+
    ylim(minlogL,maxlogL)+    
    theme_publish()+ 
    xlab(expression(log[10]("time from pulse begining (s)"))) + 
    ylab(expression(ln(Likelihood[i])))+
      
    theme(legend.position = "none",
           
         axis.title = element_text(size = 7),       # Axis titles
             axis.text = element_text(size = 7),        # Axis labels
             plot.title = element_text(size = 7),
    plot.margin = margin(
        t=0,
        r=0,
        b = 0,
        l=0,
        unit = "pt"
      ))+
    scale_color_manual(values = atp_colors)
}


fig_likelihood_pre_pulse<-function(d_x,alpha,minlogL,maxlogL){
  return(
    d_x %>%filter( beta==1,t< -0.001, scheme %in%c("scheme_10")#, iter%in%myiters[1:2]
                   )%>%
        ggplot()+
        geom_line(aes(x=-t, y=pelogL, group=interaction(i_trace,iter,i_walker),color=ATP), alpha=alpha)+
        geom_point(aes(x=-t, y=plogL, color=ATP), alpha=alpha, size=0.3)+
        theme_publish()+ 
        scale_x_reverse()+
       ylim(minlogL,maxlogL)+    
        xlab("time to pulse (s)") +
       ylab(expression(ln(Likelihood[i])))+
        theme(legend.position = "none",
         axis.title= element_text(size = 7),       # Axis titles
             axis.text = element_text(size = 7),        # Axis labels
             plot.title = element_text(size = 7, hjust = -0.35),
          plot.margin = margin(
        t=0,
        r=0,
        b = 0,
        l=0,
        unit = "pt"
      ),
          strip.text = element_text(color = "transparent"),
            strip.background = element_blank()
              )+
          scale_color_manual(values = atp_colors)
      )



}
minlogL=min(dx_s$plogL)
maxlogL=max(dx_s$plogL)


plot_grid(fig_likelihood_pre_pulse(d_x,1,minlogL,maxlogL),NULL, fig_likelihood_pulse(d_x,1,minlogL,maxlogL), nrow=1, rel_widths = c(0.5,-0.05,1))

```
```{r Fig 6, fig.width=180/25.4, fig.height=170/25.4}
figure_6p<-function(d_x, alpha){
maxVar=max(d_x$Y_var,na.rm = T )
minlogL=min(d_x$plogL,na.rm = T)
maxlogL=max(d_x$plogL,na.rm = T)

x_only_ticks=theme(axis.title.x = element_blank(), axis.text.x = element_blank())
y_only_ticks=theme(axis.title.y = element_blank(), axis.text.y = element_blank())
no_y_axis= theme( axis.text.y = element_blank(), # Removes y-axis text
         axis.title.y = element_blank(), # Removes y-axis title
          axis.ticks.y = element_blank(), 
        axis.line.y = element_blank())
no_x_axis= theme( axis.text.x = element_blank(), # Removes y-axis text
         axis.title.x = element_blank(), # Removes y-axis title
          axis.ticks.x = element_blank(), 
        axis.line.x = element_blank())
y_no_title=theme(axis.title.y = element_blank())

layout="
   ABB
   CDD
   CDD
   CDD
   CDD
   EFF
   EFF
   EFF
   EFF
   GHH
   GHH
   GHH
   GHH
   "

return(
    fig_ATP_pre_pulse(d_y) + no_x_axis+no_y_axis+ ggtitle("a") +
    fig_ATP_pulse(d_y)+ no_x_axis+no_y_axis+ ggtitle("b") +
    fig_current_pre_pulse(d_x, alpha) + x_only_ticks+
    fig_current_pulse(d_x, alpha) + x_only_ticks+
    figure_variance_pre_pulse(d_x, alpha, maxVar) + x_only_ticks + ggtitle("c")+
    figure_variance_pulse(d_x, alpha, maxVar) + x_only_ticks + no_y_axis+
    fig_likelihood_pre_pulse(d_x, alpha, minlogL, maxlogL) + ggtitle("d")+
    fig_likelihood_pulse(d_x, alpha, minlogL, maxlogL) + no_y_axis+
    plot_layout(design = layout, axes = "collect")

)
}

figure_6p(dd,0.1)
ggsave2("./r_analysis/results/Figure 6.pdf", width = 180, height = 170, units="mm")
ggsave("./r_analysis/results/Figure_6.pdf",device =cairo_pdf, dpi = 300, width = 180, height = 170 ,units = "mm")


```

```{r}
sessionInfo()
```

