---
title: "Paper Figure 1"
author: "Luciano Moffatt"
date: "2024-12-23"
output:
  pdf_document: default
  html_document: default
---



```{r setup}
library(readr)
library(tidyverse)
library(envalysis)

library(patchwork)
library(HDInterval)
library(extrafont)
#font_import(paths = "/usr/share/fonts/truetype/msttcorefonts", prompt = FALSE)
#loadfonts(device = "pdf")        # registra para pdf() y cairo_pdf()
#library(extrafont)
if (!requireNamespace("ConformationalModel", quietly = TRUE)) {
  if (!requireNamespace("devtools", quietly = TRUE)) {
    install.packages("devtools")
  }
  devtools::install_github("lmoffatt/ConformationalModel")
}
library(ConformationalModel)
library(ggimage)
```



```{r}
library(ggplot2)

```


```{r}
theme_nature_no_axis<-theme_nature()+theme(axis.line = element_blank(),  # Remove axis lines
        axis.text = element_blank(),  # Remove axis text
        axis.ticks = element_blank(), # Remove axis ticks
        axis.title = element_blank()) # Remove axis titles

```



Fist we build functions that produce the kinetic schemes drawings



```{r regular schemes}

regular_scheme_states_data_frame <- function(number_of_states, x, y, state_symbol)
{
  d_states_symbol <- data.frame(
    i_state = 1:number_of_states,
    x = x,
    y = y,
    state_symbol = state_symbol
  )
  
}

regular_scheme_arrows_data_frame <- function(d_states_symbol,
                                             i_state_from,
                                             i_state_to) {
  d_arrows = data.frame(i_state_from, i_state_to)
  
  d_arrows <- left_join(d_arrows,
                        d_states_symbol %>% select(i_state, x, y),
                        by = join_by(i_state_from == i_state)) %>%
    left_join(
      d_states_symbol %>% select(i_state, x, y),
      by = join_by(i_state_to == i_state),
      suffix = c("i", "j")
    )
}



geom_regular_scheme <- function(d_states_symbol,
                                d_arrows,
                                symbol_label_size = 8,
                                symbol_color = "black",
                                arrow_color = "black",
                                state_radius = 0.15,
                                gap = 2,
                                shift = 0.25,
                                head_size = 0.5) {
  return (
    ggplot(d_states_symbol, aes(x = x, y = y)) +
      geom_text(
        aes(label = state_symbol),
        size.unit="pt",
        parse = TRUE,
        size = symbol_label_size,
        color = symbol_color
      ) +
      geom_blank() +
      ggplot2::coord_fixed() +
    theme_nature()+
      geom_half_arrow(
        x = d_arrows$xi,
        y = d_arrows$yi ,
        xend = d_arrows$xj,
        yend = d_arrows$yj,
        color = arrow_color,
        alpha = 1,
        linetype = 1,
        linewidth = 0.1,
        gap = gap * state_radius,
        head_size = head_size * state_radius,
        shift = state_radius * shift,
        head_angle = pi / 2 / 3
      ) +
  scale_x_continuous(expand = expansion(mult = 0.1)) +  # 10% padding on x axis
  scale_y_continuous(expand = expansion(mult = 0.1)) +
      theme(
        plot.margin = margin(0, 0, 0, 0),
        # Remove all margins
        legend.position = "none",         
        axis.title = element_blank(),         
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_blank(),
        plot.background = element_blank(),
        plot.title = element_text(size=6),
        panel.background = element_blank(),
      )+theme_nature_no_axis
  )
}


```

```{r}

geom_scheme_4<-function(symbol_label_size,symbol_color="black",arrow_color="black"){
number_of_states =8
x <- c(0,1,2,3,4,5,5,6)
y <- c(0,0,0,0,0,1,-1,0)

state_symbol<-c("C[1]","CA[1]","CA[2]","CA[3]","F","O[1]","O[2]","D")
i_state_from = c(1,2,2,3,3,4,4,5,5,6,5,7,6,8,7,8)
i_state_to =   c(2,1,3,2,4,3,5,4,6,5,7,5,8,6,8,7)

d_state_symbol<-regular_scheme_states_data_frame(number_of_states,x,y,state_symbol)

d_arrows<-regular_scheme_arrows_data_frame(d_state_symbol,i_state_from, i_state_to = i_state_to)

return (
  geom_regular_scheme(d_states_symbol = d_state_symbol,d_arrows = d_arrows,symbol_label_size = symbol_label_size, symbol_color = symbol_color, arrow_color = arrow_color )

)
}
```

```{r}
geom_scheme_4(symbol_label_size = 6)
```


```{r}

geom_scheme_6 <- function(symbol_label_size=6) {
  n_conf_changes = 3
  state_symbol = c("R", "RA", "R", "F", "C", "O")
  
  pos_x_changes = c(0, 0, sqrt(0.75))
  pos_y_changes = c(0.5, -0.5, 0)
  d = 4
  delta_y_state = 0.15
  delta_x_Conf_change = 0.15
  delta_y_Conf_change = 1.5
  delta_flap_Conf_change = 0.2
  
  
  
  state_radius = 0.2
  label_color = 1
  gap = 2
  shift = 0.25
  head_size = 0.5
  sizes = 2
  
  
  i_state = 1:(2 * n_conf_changes)
  
  i_change <- 1:n_conf_changes
  
  pos_x_changes <- pos_x_changes * d
  pos_y_changes <- pos_y_changes * d
  
  
  d_changes <- data.frame(i_change, x = pos_x_changes, y = pos_y_changes)
  
  delta_y_state = delta_y_state * d
  
  delta_x_Conf_change = delta_x_Conf_change * d
  
  delta_y_Conf_change = delta_y_Conf_change * delta_y_state
  
  delta_flap_Conf_change = delta_flap_Conf_change * delta_x_Conf_change
  
  x_left_br <- c(1, 0, 0, 1) * delta_flap_Conf_change+-1 * delta_x_Conf_change
  
  y_left_br <- c(1, 1, -1, -1) * delta_y_Conf_change
  
  x_br <- rep(c(x_left_br, -x_left_br), n_conf_changes) + rep(pos_x_changes, each =
                                                                4)
  y_br <- rep(c(y_left_br, y_left_br), n_conf_changes) + rep(pos_y_changes, each =
                                                               4)
  
  i_br <- rep(i_state, each = 4)
  
  d_br <- data.frame(x = x_br, y = y_br, i_g = i_br)
  
  x <- rep(pos_x_changes, each = 2)
  y <- rep(pos_y_changes, each = 2) + rep(c(1, -1), n_conf_changes) * delta_y_state
  
  
  d_states_symbol_6 <- data.frame(i_state, x, y, state_symbol)
  #                        5       9      13      17      21
  i_state_from = c(1, 2, 3, 4, 5, 6)
  i_state_to =   c(2, 1, 4, 3, 6, 5)
  
  x_brack_subindex <- pos_x_changes + delta_x_Conf_change * (1 + 0.2)
  y_brack_subindex <- pos_y_changes - delta_y_Conf_change * (1 + 0.2)
  
  label_brack_subindex <- c("3", "", "")
  
  d_brack_sub <- data.frame(x = x_brack_subindex, y = y_brack_subindex, label = label_brack_subindex)
  
  
  i_conf_inter <- c(1, 2, 1)
  j_conf_inter <- c(2, 3, 3)
  
  label_conf_inter <- c("<<B>>", "<<C>>", "<<A>>")
  d_conf = data.frame(i_conf_inter, j_conf_inter)
  
  d_conf <- left_join(d_conf, d_changes, by = join_by(i_conf_inter == i_change)) %>%
    left_join(d_changes,
              by = join_by(j_conf_inter == i_change),
              suffix = c("i", "j"))
  
  d_conf$label = label_conf_inter
  
  d_conf$x = (d_conf$xi + d_conf$xj) * 0.5
  d_conf$y = (d_conf$yi + d_conf$yj) * 0.5
  
  dx = d_conf$xi - d_conf$xj
  dy = d_conf$yi - d_conf$yj
  angle <- atan(-dy / -dx) * 180 / pi
  
  angle <- ifelse (angle < -89, 90, angle)
  d_conf$angle <- angle
  
  
  d_arrows_6 = data.frame(i_state_from, i_state_to)
  
  d_arrows_6 <- left_join(
    d_arrows_6,
    d_states_symbol_6 %>% select(-state_symbol),
    by = join_by(i_state_from == i_state)
  ) %>%
    left_join(
      d_states_symbol_6 %>% select(-state_symbol),
      by = join_by(i_state_to == i_state),
      suffix = c("i", "j")
    )
  
  
  return (
    ggplot(d_states_symbol_6, aes(x = x, y = y)) +
      geom_text(aes(label = state_symbol),size.unit="pt",
         parse = TRUE, size = symbol_label_size) +
      geom_path(data = d_br, aes(
        x = x, y = y, group = i_g
      )) +
      geom_text(
        data = d_brack_sub,
        aes(x = x, y = y, label = label),
        size.unit="pt",
        vjust = "bottom",
        hjust = "left",
        size = symbol_label_size
      ) +
      geom_blank(data = d_brack_sub, aes(x = x, y = y)) +
      
      geom_text(
        data = d_conf,
        aes(
          x = x,
          y = y,
          label = label,
          angle = angle
        ),
        size.unit="pt",
        size = symbol_label_size
      ) +
      #ggplot2::coord_fixed() + 
      theme_nature()+
    
      theme(
        plot.margin = margin(0, 0, 0, 0),
        # Remove all margins
        panel.spacing = unit(0, "lines")  # Remove any extra panel spacing
      ) +
      geom_half_arrow(
        x = d_arrows_6$xi,
        y = d_arrows_6$yi ,
        xend = d_arrows_6$xj,
        yend = d_arrows_6$yj,
        color = "black",
        alpha = 1,
        linetype = 1,
        linewidth = 0.3,
        gap = gap * state_radius,
        head_size = head_size * state_radius,
        shift = state_radius * shift,
        head_angle = pi / 2 / 3
      ) +
      theme(
        legend.position = "none",         
        axis.title = element_blank(),         
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_blank(),
        plot.background = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(size=6),
        plot.margin = margin(0, 0, 0, 0)
      )
  )
}


```




```{r}

geom_scheme_7 <- function(symbol_label_size = 6) {
  state_radius = 0.2
  label_color = 1
  gap = 2
  shift = 0.25
  head_size = 0.5
  sizes = 2
  
  n_conf_changes = 3
  
  i_state = 1:(2 * n_conf_changes)
  
  i_change <- 1:n_conf_changes
  
  
  d = 4
  pos_x_changes <- c(-0.5, 0, 0.5) * d
  pos_y_changes <- c(0, sqrt(0.75), 0) * d
  
  pos_x_changes <- c(0, 0, sqrt(0.75)) * d
  pos_y_changes <- c(0.45, -0.45, 0) * d
  
  d_changes <- data.frame(i_change, x = pos_x_changes, y = pos_y_changes)
  delta_y_state = 0.15 * d
  
  delta_x_Conf_change = 0.15 * d
  
  delta_y_Conf_change = 1.5 * delta_y_state
  
  delta_flap_Conf_change = 0.2 * delta_x_Conf_change
  
  x_left_br <- c(1, 0, 0, 1) * delta_flap_Conf_change+-1 * delta_x_Conf_change
  
  y_left_br <- c(1, 1, -1, -1) * delta_y_Conf_change
  
  x_br <- rep(c(x_left_br, -x_left_br), n_conf_changes) + rep(pos_x_changes, each =
                                                                4)
  y_br <- rep(c(y_left_br, y_left_br), n_conf_changes) + rep(pos_y_changes, each =
                                                               4)
  
  i_br <- rep(i_state, each = 4)
  
  d_br <- data.frame(x = x_br, y = y_br, i_g = i_br)
  
  
  x_left_br <- c(1, 0, 0, 1) * delta_flap_Conf_change * 1.1+-1.3 * delta_x_Conf_change
  
  y_left_br <- c(1, 1, -1, -1) * (delta_y_Conf_change * 1.3 + d * 0.45)
  
  x_br <- c(x_left_br, -x_left_br) + pos_x_changes[1] * 0.5 + pos_x_changes[2] *
    0.5
  y_br <- c(y_left_br, y_left_br) +  pos_y_changes[1] * 0.5 + pos_y_changes[2] *
    0.5
  i_br <- rep(c(1, 2), each = 4)
  
  d_giant_br <- data.frame(x = x_br, y = y_br, i_g = i_br)
  
  
  x <- rep(pos_x_changes, each = 2)
  y <- rep(pos_y_changes, each = 2) + rep(c(1, -1), n_conf_changes) * delta_y_state
  
  
  state_symbol <- c("R", "RA", "R", "F", "C", "O")
  
  
  
  d_states_symbol_6 <- data.frame(i_state, x, y, state_symbol)
  #                        5       9      13      17      21
  i_state_from = c(1, 2, 3, 4, 5, 6)
  i_state_to =   c(2, 1, 4, 3, 6, 5)
  
  x_brack_subindex <- pos_x_changes + delta_x_Conf_change * 1.2 * (1 + 0.2)
  y_brack_subindex <- pos_y_changes - delta_y_Conf_change * 1.2 * (1 + 0.2)
  
  label_brack_subindex <- c("", "3", "")
  
  d_brack_sub <- data.frame(x = x_brack_subindex, y = y_brack_subindex, label = label_brack_subindex)
  
  
  i_conf_inter <- c(1, 2, 1)
  j_conf_inter <- c(2, 3, 3)
  
  label_conf_inter <- c("<<B>>", "<<C>>", "<<A>>")
  d_conf = data.frame(i_conf_inter, j_conf_inter)
  
  d_conf <- left_join(d_conf, d_changes, by = join_by(i_conf_inter == i_change)) %>%
    left_join(d_changes,
              by = join_by(j_conf_inter == i_change),
              suffix = c("i", "j"))
  
  d_conf$label = label_conf_inter
  
  d_conf$x = (d_conf$xi + d_conf$xj) * 0.5
  d_conf$y = (d_conf$yi + d_conf$yj) * 0.5
  
  dx = d_conf$xi - d_conf$xj
  dy = d_conf$yi - d_conf$yj
  angle <- atan(-dy / -dx) * 180 / pi
  
  angle <- ifelse (angle < -89, 90, angle)
  d_conf$angle <- angle
  
  
  d_arrows_6 = data.frame(i_state_from, i_state_to)
  
  d_arrows_6 <- left_join(
    d_arrows_6,
    d_states_symbol_6 %>% select(-state_symbol),
    by = join_by(i_state_from == i_state)
  ) %>%
    left_join(
      d_states_symbol_6 %>% select(-state_symbol),
      by = join_by(i_state_to == i_state),
      suffix = c("i", "j")
    )
  
  return (
    ggplot(d_states_symbol_6, aes(x = x, y = y)) +
      geom_text(aes(label = state_symbol),size.unit="pt",
         parse = TRUE, size = symbol_label_size) +
      geom_path(data = d_br, aes(
        x = x, y = y, group = i_g
      )) +
      geom_path(data = d_giant_br, aes(
        x = x, y = y, group = i_g
      )) +
      geom_text(
        data = d_brack_sub,
        aes(x = x, y = y, label = label),
        size.unit="pt",
        vjust = "bottom",
        hjust = "left",
        size = symbol_label_size
      ) +
      geom_blank(data = d_brack_sub, aes(x = x, y = y)) +
      
      geom_text(
        data = d_conf,
        aes(
          x = x,
          y = y,
          label = label,
          angle = angle
        ),
        size.unit="pt",
        size = symbol_label_size
      ) +theme_nature()+
    
      #ggplot2::coord_fixed() +
      theme(
        plot.margin = margin(0, 0, 0, 0),
        # Remove all margins
        panel.spacing = unit(0, "lines")  # Remove any extra panel spacing
      ) +
      geom_half_arrow(
        x = d_arrows_6$xi,
        y = d_arrows_6$yi ,
        xend = d_arrows_6$xj,
        yend = d_arrows_6$yj,
        color = "black",
        alpha = 1,
        linetype = 1,
        linewidth = 0.3,
        gap = gap * state_radius,
        head_size = head_size * state_radius,
        shift = state_radius * shift,
        head_angle = pi / 2 / 3
      ) +theme_nature()+
    
      theme(
        legend.position = "none",
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_blank(),
        plot.background = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(size=6),
       plot.margin = margin(0, 0, 0, 0)
      )
  )
}



```




a function for conformational schemes

```{r}
geom_conformational_scheme <- function(label_conf_inter,color_scale,symbol_label_size= 5, label_conf_inter_3=c()) {
  state_radius = 0.25
  label_color = 1
  gap = 1
  shift = 0.25
  head_size = 0.5
  sizes = 2
  
  n_conf_changes = 3
  
  i_state = 1:(2 * n_conf_changes)
  
  i_change <- 1:n_conf_changes
  
  
  d = 4
  conf_radius = 4
  
  pos_x_changes <- c(-0.5, 0, 0.5) * d
  pos_y_changes <- c(0, -0.75, 0) * d
  
  #pos_x_changes<-c(0,0,sqrt(0.75))*d
  #pos_y_changes<-c(0.45,-0.45,0)*d
  
  d_changes <- data.frame(i_change, x = pos_x_changes, y = pos_y_changes)
  delta_y_state = 0.03 * d * conf_radius
  
  delta_x_Conf_change = 0.025 * d * conf_radius
  
  delta_y_Conf_change = 1.5 * delta_y_state
  
  delta_flap_Conf_change = 0.2 * delta_x_Conf_change
  
  x_left_br <- c(1, 0, 0, 1) * delta_flap_Conf_change+-1 * delta_x_Conf_change
  
  y_left_br <- c(1, 1, -1, -1) * delta_y_Conf_change
  
  x_br <- rep(c(x_left_br, -x_left_br), n_conf_changes) + rep(pos_x_changes, each =
                                                                4)
  y_br <- rep(c(y_left_br, -y_left_br), n_conf_changes) + rep(pos_y_changes, each =
                                                               4)
  
  i_br <- rep(i_state, each = 4)
  
  d_br <- data.frame(x = x_br, y = y_br, i_g = i_br)
  
  
  x_left_br <- c(1, 0, 0, 1) * delta_flap_Conf_change * 3 + 0 * delta_x_Conf_change
  
  y_left_br <- c(1, 1, -1, -1) * (delta_y_Conf_change * 1.25 + d * 0.45)
  
  x_br <- c(x_left_br + pos_x_changes[1], -x_left_br + pos_x_changes[3])
  y_br <- c(y_left_br, y_left_br) +  pos_y_changes[1] * 0.5 + pos_y_changes[2] *
    0.5
  i_br <- rep(c(1, 2), each = 4)
  
  d_giant_br <- data.frame(x = x_br, y = y_br, i_g = i_br)
  
  x_brack_subindex <- c(x_br[6] + delta_flap_Conf_change * 2*0.6)
  y_brack_subindex <- c(y_br[7] - delta_flap_Conf_change * 2*0.6)
  
  label_brack_subindex <- c("3")
  
  d_brack_sub <- data.frame(x = x_brack_subindex, y = y_brack_subindex, label = label_brack_subindex)
  
  
  
  x <- rep(pos_x_changes, each = 2)
  y <- rep(pos_y_changes, each = 2) + rep(c(1, -1), n_conf_changes) * delta_y_state
  
  
  state_symbol <- c("R", "F", "R", "RA", "R", "F")
  
  
  
  d_states_symbol_6 <- data.frame(i_state, x, y, state_symbol)
  #                        5       9      13      17      21
  i_state_from = c(1, 2, 3, 4, 5, 6)
  i_state_to =   c(2, 1, 4, 3, 6, 5)
  
  
  
  i_conf_inter <- c(1, 2)
  j_conf_inter <- c(2, 3)
  
  
  d_conf = data.frame(i_conf_inter, j_conf_inter)
  
  d_conf <- left_join(d_conf, d_changes, by = join_by(i_conf_inter == i_change)) %>%
    left_join(d_changes,
              by = join_by(j_conf_inter == i_change),
              suffix = c("i", "j"))
  
  d_conf$label = label_conf_inter
  
  
  d_conf$x = (d_conf$xi + d_conf$xj) * 0.5
  d_conf$y = (d_conf$yi + d_conf$yj) * 0.5
  
  dx = d_conf$xi - d_conf$xj
  dy = d_conf$yi - d_conf$yj
  angle <- atan(-dy / -dx) * 180 / pi
  
  angle <- ifelse (angle < -89, 90, angle)
  d_conf$angle <- angle
  
  
  
  d_conf_3<-data.frame()
  
  d_conf_3<-data.frame(x = numeric(0), y = numeric(0), label = character(0))
  
  d_lab_conf_3<-data.frame(x = numeric(0), y = numeric(0), label = character(0), angle=numeric(0))
  
  if (length(label_conf_inter_3)>0){
  i_conf_inter <- c(1)
  j_conf_inter <- c(2)
  k_conf_inter <- c(3)
  d_conf_3 = data.frame(i_conf_inter, j_conf_inter, k_conf_inter)
  
  
  
  
  d_conf_3 <- left_join(d_conf_3, d_changes, by = join_by(i_conf_inter == i_change)) %>%
    left_join(d_changes,
              by = join_by(j_conf_inter == i_change),
              suffix = c("i", "j")) %>%
    left_join(d_changes, by = join_by(k_conf_inter == i_change))
  d_conf_3$xk = d_conf_3$x
  d_conf_3$yk = d_conf_3$y
  
  d_conf_3$label = label_conf_inter_3
  
  
  d_conf_3$x = (d_conf_3$xi + d_conf_3$xj + d_conf_3$x) / 3
  d_conf_3$y = (d_conf_3$yi + d_conf_3$yj + d_conf_3$yk) / 3
  
  calc_angle <- function(dx, dy) {
    angle <- atan(-dy / -dx) * 180 / pi
    angle <- ifelse(angle < -89, 90, angle)
    return (angle)
  }
  
  lab_3_radius = 0.33
  x_pos_lab_3 <- c(
    d_conf_3$x + lab_3_radius * (d_conf_3$xi - d_conf_3$x) ,
    d_conf_3$x + lab_3_radius * (d_conf_3$xj - d_conf_3$x) ,
    d_conf_3$x + lab_3_radius * (d_conf_3$xk - d_conf_3$x)
  )
  
  y_pos_lab_3 <- c(
    d_conf_3$y + lab_3_radius * (d_conf_3$yi - d_conf_3$y) ,
    d_conf_3$y + lab_3_radius * (d_conf_3$yj - d_conf_3$y) ,
    d_conf_3$y + lab_3_radius * (d_conf_3$yk - d_conf_3$y)
  )
  
  angle_lab_3 <- c(calc_angle((d_conf_3$xi - d_conf_3$x), (d_conf_3$yi - d_conf_3$y)) , calc_angle((d_conf_3$xj -
                                                                                                      d_conf_3$x), (d_conf_3$yj - d_conf_3$y)) , calc_angle((d_conf_3$xk - d_conf_3$x), (d_conf_3$yk -
                                                                                                                                                                                           d_conf_3$y)))
  
  lab_3 <- c("<<", "<<", ">>")
  
  d_lab_conf_3 = data.frame(
    x = x_pos_lab_3,
    y = y_pos_lab_3,
    label = lab_3,
    angle = angle_lab_3
  )
  
  }
  
  dx = d_conf$xi - d_conf$xj
  dy = d_conf$yi - d_conf$yj
  angle <- atan(-dy / -dx) * 180 / pi
  
  angle <- ifelse (angle < -89, 90, angle)
  
  
  
  d_arrows_6 = data.frame(i_state_from, i_state_to)
  
  d_arrows_6 <- left_join(
    d_arrows_6,
    d_states_symbol_6 %>% select(-state_symbol),
    by = join_by(i_state_from == i_state)
  ) %>%
    left_join(
      d_states_symbol_6 %>% select(-state_symbol),
      by = join_by(i_state_to == i_state),
      suffix = c("i", "j")
    )
  
  
  return (
    ggplot(d_states_symbol_6, aes(x = x, y = y)) +
      geom_path(
        data = d_giant_br,
        aes(x = x, y = y, group = i_g),
        linetype = "dotted", 
        linewidth = 0.5
      ) +
      geom_polygon(data = d_br, aes(
        x = x, y = y
      ), fill="white", linetype="blank") +
     geom_text(
        aes(label = state_symbol),
        size.unit="pt",
        parse = FALSE,
        size = symbol_label_size
      ) +
      geom_path(data = d_br, aes(
        x = x, y = y, group = i_g
      )) +
        geom_text(
        data = d_brack_sub,
        aes(x = x, y = y, label = label),
        size.unit="pt",
        vjust = "bottom",
        hjust = "left",
        size = symbol_label_size
      ) +
      geom_blank(data = d_brack_sub, aes(x = x, y = y)) +
      
      geom_text(
        data = d_conf,
        aes(
          x = x,
          y = y,
          label = label,
          angle = angle 
        ),
        size.unit="pt",
        size = symbol_label_size
      ) +
      geom_text(
        data = d_conf_3,
        aes(x = x, y = y, label = label
            ),
        size.unit="pt",
        vjust = "top",
        size = symbol_label_size
      ) +
      geom_text(
        data = d_lab_conf_3,
        aes(
          x = x,
          y = y,
          label = label,
          angle = angle
        ),
        size.unit="pt",
        size =symbol_label_size
      ) +
      scale_color_manual(values=color_scale)+theme_nature()+
    
      
      #ggplot2::coord_fixed() +  
      theme(
        plot.margin = margin(0, 0, 0, 0),
        # Remove all margins
        panel.spacing = unit(0, "lines")  # Remove any extra panel spacing
      ) +
      geom_half_arrow(
        x = d_arrows_6$xi,
        y = d_arrows_6$yi ,
        xend = d_arrows_6$xj,
        yend = d_arrows_6$yj,
        color = "black",
        alpha = 1,
        linetype = 1,
        linewidth = 0.3,
        gap = gap * state_radius,
        head_size = head_size * state_radius,
        shift = state_radius * shift,
        head_angle = pi / 2 / 3
      ) +theme_nature()+
    
      theme(
        legend.position = "none",         
        axis.title = element_blank(),         
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_blank(),
        plot.background = element_blank(),
        panel.background = element_blank(),
         plot.title = element_text(size=6),
       plot.margin = margin(0, 0, 0, 0)
      )
  )
  
}
```


scheme 11 was not included in the manuscript

```{r}

interaction_color_scale=c("<<RB>>"="#cc79a7","<<BR>>"="#0072b2" , "RBR"="#56b4e9" )
geom_scheme_11<-function(symbol_label_size= 6){
  label_conf_inter <- c("<<RB>>", "<<BR>>")
  
  label_conf_inter_3 <- c("RBR")
  
  return (geom_conformational_scheme(label_conf_inter = label_conf_inter,
                                     color_scale = interaction_color_scale,
                                    symbol_label_size = symbol_label_size,
                                    label_conf_inter_3 = label_conf_inter_3)
  )
  
}

geom_scheme_10<-function(symbol_label_size= 6){
  label_conf_inter <- c("<<RB>>", "<<BR>>")
  
  label_conf_inter_3 <- c()
  
  return (geom_conformational_scheme(label_conf_inter = label_conf_inter,
                                     color_scale = interaction_color_scale,
                                    symbol_label_size = symbol_label_size,
                                    label_conf_inter_3 = label_conf_inter_3)
  )
  
}

geom_scheme_9<-function(symbol_label_size= 6){
  label_conf_inter <- c("<<RB>>", "<<RB>>")
  
  label_conf_inter_3 <- c()
  
  return (geom_conformational_scheme(label_conf_inter = label_conf_inter,
                                     color_scale = interaction_color_scale,
                                    symbol_label_size = symbol_label_size,
                                    label_conf_inter_3 = label_conf_inter_3)
  )
  
  
}



```



```{r, fig.width=25/24.5, fig.height=35/24.5}
geom_scheme_6(symbol_label_size = 6)+ggtitle("scheme VII")+theme(plot.title = element_text(size=6))
```

```{r, fig.width=25/24.5, fig.height=35/24.5}
geom_scheme_7(symbol_label_size = 6)+ggtitle("scheme VII")+theme(plot.title = element_text(size=6))
```


```{r, fig.width=30/24.5, fig.height=30/24.5}
geom_scheme_11(symbol_label_size = 6)+ggtitle("scheme 6")+theme(plot.title = element_text(size=6))
```
```{r, fig.width=30/24.5, fig.height=30/24.5}
geom_scheme_10(symbol_label_size = 6)+ggtitle("scheme 6")+theme(plot.title = element_text(size=6))
```




```{r, fig.width=30/24.5, fig.height=30/24.5}
geom_scheme_9(symbol_label_size = 6)+ggtitle("scheme 6")+theme(plot.title = element_text(size=6))
```


```{r, fig.width=50/24.5, fig.height=35/24.5}

(geom_scheme_6(symbol_label_size = 6)+ggtitle("Scheme VI") |geom_scheme_7(symbol_label_size = 6)+ggtitle("Scheme VII"))
```


We finished defining the scheme drawings. 

Now we load the files. 







```{r}
filename="r_analysis/data/mcmc_analisis.csv"
d=read.csv(filename)
```

```{r}
df<-d%>%select(iter_cat,mean,sd,ess_bulk,ess_tail,scheme,algorithm)%>%mutate(ess=pmin(ess_bulk,ess_tail))%>%select(-ess_bulk,-ess_tail)%>%
    pivot_wider(names_from = iter_cat, values_from = c(mean,sd,ess))%>%
  mutate(mean=ifelse(ess_6>ess_8, mean_6,mean_8),sd=ifelse(ess_6>ess_8, sd_6/ess_6^0.5,sd_8/ess_8^0.5),ess=ifelse(ess_6>ess_8, ess_6,ess_8),.keep = "unused")
```


A function that produces the Evidence plot for the recursive algorithm 
(DR is because of double recursive, because it considers two points (start and end))
Note: as we removed scheme_7 and scheme_11 from the analysis, there is a shift in the scheme numbering

```{r}
Fig_Ev_DR<-function(){


df%>%filter(algorithm=="DR",
                    scheme%in% c("scheme_4_inactd","scheme_9_inact","scheme_10_inactd","scheme_6_inactd",
         # "scheme_7_inactd",
          "scheme_7_inacts"))->d_e

d_e<-d_e%>%
  mutate(
    scheme_label = recode(scheme,
                          "scheme_10_inactd" = "IX",
                          "scheme_4_inact" = "IVt",
                          "scheme_4_inactd" = "IV",
                          "scheme_9_inact" = "VIII",
                          #"scheme_11_inactd" = "XI",
                          "scheme_6_inactd" = "VI",
                          "scheme_7_inacts" = "VII",
                          "scheme_7_inactd" = "VIId")
  )


d_e%>%arrange(mean)->d_e

d_e$order=1:nrow(d_e)
# Define buffer to add space on the y-axis
buffer <- 0.1 * diff(range(d_e$mean))
x_min <- min(d_e$mean-d_e$sd) - buffer
x_max <- max(d_e$mean + d_e$sd) + buffer

# Plot using geom_rect with custom y-axis limits
pos_lab_x=(d_e%>%filter(scheme=="scheme_10_inactd"))$mean[1]
pos_lab_y=13

loge_substantial=log(10^0.5)
loge_strong=log(10)
loge_verystrong=log(100^0.5)
loge_decisive= log(100)



d_e%>%ggplot() +
  geom_rect(aes(
    ymin = order - 0.4,  # Adjust bar width
    ymax = order + 0.4,
    xmin = mean - sd,  # Set bar base to y_min
    xmax = x_max, 
    fill = "error"
  )) +
  geom_rect(aes(
    ymin = order - 0.4,  # Adjust bar width
    ymax = order + 0.4,
    xmin = mean + sd,  # Set bar base to y_min
    xmax = x_max, 
    fill =scheme
  )) +
  scale_fill_manual(values = c(
    "error" = "grey",
    "scheme_10_inact" = "#0072b2",  # Dark blue
    "scheme_10_inactd" = "#0072b2",  # Dark blue
    "scheme_4_inactd" = "#d55e00",   # Medium green
    "scheme_4_inact" = "#d55e00",   # Medium green
    "scheme_9_inactd" = "#cc79a7",   # Orange
    "scheme_9_inact" = "#cc79a7",   # Orange
   # "scheme_11_inactd" = "#56b4e9",  # Purple
    "scheme_6_inactd" = "#f0e442",   # Red
    "scheme_7_inact" = "#e69f00",    # Yellow
    "scheme_7_inactd" = "#e69f00",    # Yellow
    "scheme_7_inacts" = "#e69f00"    # Yellow
  ))+
  scale_y_continuous(breaks = 1:length(d_e$scheme), labels = d_e$scheme_label) +
  scale_x_continuous(limits = c(x_min, x_max)) +
  labs(x ="ln(Evidence)", y = "Scheme") +
  theme_nature() + # base font size for a Nature-style look
  theme(
    axis.title = element_text(size = 7),       # Axis titles
    axis.text = element_text(size = 6),        # Axis labels
    legend.text = element_text(size = 6),      # Legend text
    legend.title = element_blank(),             # Nature prefers no legend title
    plot.title = element_text(size = 7),        # Optional plot title, if needed
    legend.position = "none"  
    )#+ggtitle("Recursive algorithm")
}
Fig_Ev_DR()
```


this function produces the evidence plot for the non recursive algorithm 

```{r}

Fig_Ev_SNR<-function(){

df%>%filter(algorithm=="DNR",
                    scheme%in%c("scheme_4_inact","scheme_6_inact","scheme_7_inacts","scheme_9_inact","scheme_10_inact"))->d_e

d_e<-d_e%>%
  mutate(
    scheme_label = recode(scheme,
                          "scheme_10_inact" = "IX",
                          "scheme_4_inact" = "IV",
                          "scheme_9_inact" = "VIII",
                          #"scheme_11_inact" = "XI",
                          "scheme_6_inact" = "VI",
                          "scheme_7_inacts" = "VII")
  )

d_e%>%arrange(mean)->d_e
d_e$order=1:nrow(d_e)
# Define buffer to add space on the y-axis
buffer <- 0.1 * diff(range(d_e$mean))
x_min <- min(d_e$mean - d_e$sd ) - buffer
x_max <- max(d_e$mean + d_e$sd) + buffer

# Plot using geom_rect with custom y-axis limits
pos_lab_x=(d_e%>%filter(scheme=="scheme_10"))$mean[1]
pos_lab_y=13

loge_substantial=log(10^0.5)
loge_strong=log(10)
loge_verystrong=log(100^0.5)
loge_decisive= log(100)



d_e%>%ggplot() +
  geom_rect(aes(
    ymin = order - 0.4,  # Adjust bar width
    ymax = order + 0.4,
    xmin = mean-sd,  # Set bar base to y_min
    xmax = x_max, 
    fill = "error"
  ), fill = "grey") +
  geom_rect(aes(
    ymin = order - 0.4,  # Adjust bar width
    ymax = order + 0.4,
    xmin = mean+sd,  # Set bar base to y_min
    xmax = x_max, 
    fill =scheme
  )) +
  scale_fill_manual(values = c(
    "error" = "grey",
    "scheme_10_inact" = "#0072b2",  # Dark blue
    "scheme_10_inactd" = "#0072b2",  # Dark blue
    "scheme_4_inactd" = "#d55e00",   # Medium green
    "scheme_4_inact" = "#d55e00",   # Medium green
    "scheme_9_inactd" = "#cc79a7",   # Orange
    "scheme_9_inact" = "#cc79a7",   # Orange
    "scheme_11_inactd" = "#56b4e9",  # Purple
    "scheme_11_inact" = "#56b4e9",  # Purple
    "scheme_6_inactd" = "#f0e442",   # Red
    "scheme_6_inact" = "#f0e442",   # Red
    "scheme_7_inact" = "#e69f00",    # Yellow
    "scheme_7_inactd" = "#e69f00",    # Yellow
    "scheme_7_inacts" = "#e69f00"    # Yellow
  ))+
  scale_y_continuous(breaks = 1:length(d_e$scheme), labels = paste0(d_e$scheme_label)) +
  scale_x_continuous(limits = c(x_min, x_max)) +
  labs(x = "ln(Evidence)", y = "Scheme") +
  theme_nature() + # base font size for a Nature-style look
  theme(
    axis.title = element_text(size = 7),       # Axis titles
    axis.text = element_text(size = 6),        # Axis labels
    legend.text = element_text(size = 6),      # Legend text
    legend.title = element_blank(),             # Nature prefers no legend title
    legend.position = "none",
    plot.title = element_text(size = 7)        # Optional plot title, if needed
  )#+ggtitle("Non-Recursive algorithm")
}
```






```{r Figure 1, fig.width=180/24.5, fig.height=120/24.5}
# Load necessary libraries
library(ggplot2)
library(cowplot)


# Example of creating panel plots (assuming they are defined earlier)
#

panel_A <- (geom_scheme_9() +theme_nature_no_axis+ ggtitle("a",subtitle = "Scheme VIII"))+theme(plot.title = element_text(size=7, hjust = -0.02), plot.subtitle = element_text(size=6)) + 
  (geom_scheme_10() +theme_nature_no_axis+ ggtitle("",subtitle ="Scheme IX")) + theme(plot.title = element_text(size=7, hjust = -0.1, vjust=-0.1), plot.subtitle = element_text(size=6))+ 
#  (geom_scheme_11()+theme_nature_no_axis + ggtitle("",subtitle ="Scheme XI"))+ theme(plot.title = element_text(size=7, hjust = -0.1, vjust=-0.1), plot.subtitle = element_text(size=6)) + 
  plot_layout(ncol = 1)

panel_B <- plot_grid(geom_scheme_4(symbol_label_size = 6) +theme_nature_no_axis+ 
                       ggtitle("b",subtitle = "Scheme IV")+theme(plot.title = element_text(size=7, hjust = -0.02, vjust=-0.5), plot.subtitle = element_text(size=6)), 
  (geom_scheme_6(symbol_label_size = 6) +theme_nature_no_axis+ 
     ggtitle("c",subtitle = "Scheme VI")+theme(plot.title = element_text(size=7, hjust = -0.02), plot.subtitle = element_text(size=6)))+
  (geom_scheme_7(symbol_label_size = 6) +theme_nature_no_axis+ 
     ggtitle("",subtitle = "Scheme VII")+theme(plot.title = element_text(size=7, hjust = -0.02), plot.subtitle = element_text(size=6))), nrow=1)

panel_C <- Fig_Ev_DR() + 
  ggtitle("d", subtitle="Recursive")+ theme(plot.title = element_text(size=7, hjust = -0.1, vjust=-0.1), plot.subtitle = element_text(size=6))+ 
  Fig_Ev_SNR() +  
  ggtitle("e", subtitle="Non-Recursive")+ theme(plot.title = element_text(size=7, hjust = -0.1, vjust=-0.1), plot.subtitle = element_text(size=6)) + 
  plot_layout(ncol = 2)

panel_B_C<-plot_grid(panel_B,panel_C , nrow=2, rel_heights = c(0.7,1))

# Combine the panels using cowplot's plot_grid() function
combined_plot <- plot_grid(panel_A, panel_B_C, 
                           ncol = 2,                    # Arrange plots side-by-side in 3 columns
                           rel_widths = c(0.4,1))      # Control relative width of each column

# Show the combined plot
combined_plot
ggsave("./r_analysis/results/Figure_1.pdf",
       combined_plot,
       device = cairo_pdf,
       family = "Arial",
       width = 180, height = 120, units = "mm", dpi = 300)
```


```{r}
sessionInfo()
```


